---
title: "Maps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{maps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tuichartr)
library(rnaturalearth)
```


You can make continuous maps with `tuichartr` and `tuimaps` function. It works with `sf` objects, we'll use package [`rnaturalearth`](https://github.com/ropensci/rnaturalearth) to retrieves shapes.

Mapping for creating a map require **3** aesthetics:

* *code*: a unique identifiers for polygons
* *label*: a label for the polygon, this is the name that will be displayed on tooltip.
* *value*: a numeric variable to color the polygons


```{r}
# Retrieve Italy polygons
italy <- ne_states("italy", returnclass = "sf")
# add a random numeric variable
italy$random <- sample(1:100, nrow(italy), TRUE)

# draw map
tuimap(width = 500, height = 500) %>% 
  add_map_data(italy, aes(code = adm1_code, label = name, value = random)) %>% 
  tui_chart(title = "Italy map")
```


An other example, with some options:

```{r}
africa <- ne_countries(continent = "africa", returnclass = "sf")
africa$random <- sample(1:100, nrow(africa), TRUE)

tuimap(width = 700, height = 900) %>% 
  add_map_data(africa, aes(code = sov_a3, label = name, value = random)) %>% 
  tui_chart(
    title = "Africa map",
    format = JS("function(value) {return value + '%'}")
  ) %>% 
  tui_theme(
    series = list(
      startColor = "#DEEBF7",
      endColor = "#084594"
    )
  )
```





